Computer Science House Constitution

### 2013-12-14 articles.tex
renamed constitution to articles

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second position.
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
\end{enumerate}

@@

\asection{Selection}
\asubsection{Dual Directorship}
Social Director and Research and Development Director are the only Executive Board positions that allow for Dual Directorship. If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot. If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative. Each different nomination must be a separate entry on the election ballot.

>>>>

\asection{Qualifications}
\asubsection{Qualifications to be the Chairman, Evaluations Director, Social Director(s), Financial Director, Research and Development Director(s), House Improvements Director, House History Director}
\begin{enumerate}
	\item Candidates must be Active Members during the term of office.
	\item Candidates must have at least one full semester of House membership as an Active Member.
	\item Elected or selected candidates may not hold two simultaneous voting Executive Board positions, and must therefore resign their current position or decline a second position should they be elected or selected to a second voting position.
\end{enumerate}
\asubsection{Qualifications to be the Operational Communications Director}
\begin{enumerate}
	\item Candidates must be a current Root Type Person \ref{Operations of the Operational Communications Directorship}
	\item Candidates must be a current Active Member.
	\item A Root Type Person cannot be the director if they currently hold any other Executive Board Position.
\end{enumerate}

@@

\asection{Selection}
\asubsection{Dual Directorship}
Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship. If two candidates elect to run as a Dual Directorship, their names are placed together on a single line of the election ballot. If they are also nominated as a normal directorship or as a dual directorship with another House member, their votes are not cumulative. Each different nomination must be a separate entry on the election ballot. 
Non-voting Executive Board positions (i.e. Ad-Hoc Directors) are not restricted to to single or dual directorship.
